Squintability and Other Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2025-03-03 jso.qmd
fix references

The R packages used in this work include: `tidyverse` [@tidyverse];
`patchwork` [@patchwork]; `ggh4x` [@ggh4x]; `broom` [@broom]; 
`kableExtra` [@kabelextra]; `ferrn` [@RJ-2021-105]; and `cassowaryr` [@cassowaryr].

>>>>

The R packages used in this work include: `tidyr` [@tidyr], `dplyr` [@dplyr], 
`ggplot2` [@ggplot2], `knitr` [@knitr],`gtsummary` [@gtsummary],
`patchwork` [@patchwork], `ggh4x` [@ggh4x], `broom` [@broom], 
`kableExtra` [@kabelextra], `ferrn` [@RJ-2021-105], and `cassowaryr` [@cassowaryr].

### 2025-03-03 jso.tex
fix references

Optimisation of PP is often discussed when new indexes are proposed
(Posse 1995; Marie-Sainte, Berro, and Ruiz-Gazen 2010; Grochowski and
Duch 2011). Cook et al. (1995) tied the optimisation more closely to the
index, when they introduced the PPGT, which monitors the optimisation
visually so that the user can see the projected data leading in and out
of the optimum. An implementation is available in the \texttt{tourr}
package (H. Wickham et al. 2011) in R (R Core Team 2023). Zhang et al.
(2021) illustrated how to diagnose optimisation processes, particularly
focusing on the guided tour, and revealed a need for improved
optimisation. While improving the quality of the optimisation solutions
in the tour is essential, it is also important to be able to view the
data projections as the optimisation progresses. Integrating the guided
tour with a global optimisation algorithm that is efficient in finding
the global optimal and enables viewing of the projected data during the
exploration process is a goal.

@@

There are numerous PP index functions available: introduced in Huber
(1985), Cook, Buja, and Cabrera (1993), Lee et al. (2005), Lee and Cook
(2010), Grimm (2016), Ursula Laa and Valencia (2022). Most are
relatively simply defined, for any projection dimension, and implemented
because they are relatively easy to optimise. A goal is to develop PP
indexes based on scagnostics Leland Wilkinson and Wills (2008), but the
blockage is their optimisation as these tend to be noisy, with
potentially small squint angles.

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, coltitle=black, breakable, opacityback=0, rightrule=.15mm, colframe=quarto-callout-note-color-frame, left=2mm, toprule=.15mm, toptitle=1mm, bottomtitle=1mm, arc=.35mm, opacitybacktitle=0.6, colbacktitle=quarto-callout-note-color!10!white, bottomrule=.15mm, titlerule=0mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, leftrule=.75mm]

@@

The R packages used in this work include: \texttt{tidyverse} (Hadley
Wickham et al. 2019); \texttt{patchwork} (Pedersen 2024); \texttt{ggh4x}
(van den Brand 2024); \texttt{broom} (Robinson, Hayes, and Couch 2024);
\texttt{kableExtra} (Zhu 2024); \texttt{ferrn} (Zhang et al. 2021); and
\texttt{cassowaryr} (Mason et al. 2022).

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-abdulah2023large}
Abdulah, Sameh, Yuxiao Li, Jian Cao, Hatem Ltaief, David Keyes, Marc
Genton, and Ying Sun. 2023. {``Large-Scale Environmental Data Science
with {ExaGeoStatR}.''} \emph{Environmetrics} 34 (1): e2770.
\url{https://doi.org/10.1002/env.2770}.

\bibitem[\citeproctext]{ref-adams2003sobolev}
Adams, Robert, and John Fournier. 2003. \emph{Sobolev Spaces}. Vol. 140.
Pure and Applied Mathematics. Elsevier.

\bibitem[\citeproctext]{ref-Allaire_Quarto_2022}
Allaire, J. J., Charles Teague, Carlos Scheidegger, Yihui Xie, and
Christophe Dervieux. 2022. \emph{{Quarto}} (version 1.2).
\url{https://doi.org/10.5281/zenodo.5960048}.

\bibitem[\citeproctext]{ref-Bertsimas93}
Bertsimas, Dimitris, and John Tsitsiklis. 1993. {``{Simulated
Annealing}.''} \emph{Statistical Science} 8 (1): 10--15.
\url{https://doi.org/10.1214/ss/1177011077}.

\bibitem[\citeproctext]{ref-chou_novel_2021}
Chou, Jui-Sheng, and Dinh-Nhat Truong. 2021. {``A Novel Metaheuristic
Optimizer Inspired by Behavior of Jellyfish in Ocean.''} \emph{Applied
Mathematics and Computation} 389 (January): 125535.
\url{https://doi.org/10.1016/j.amc.2020.125535}.

@@

\bibitem[\citeproctext]{ref-Grimm2016}
Grimm, Katrin. 2016. {``Kennzahlenbasierte Grafikauswahl.''} Doctoral
thesis, Universit{ä}t Augsburg.

\bibitem[\citeproctext]{ref-grochowski2011}
Grochowski, Marek, and Włodzisław Duch. 2011. {``Fast Projection Pursuit
Based on Quality of Projected Clusters.''} In \emph{Adaptive and Natural
Computing Algorithms}, edited by Andrej Dobnikar, Uroš Lotrič, and
Branko Šter, 89--97. Berlin, Heidelberg: Springer Berlin Heidelberg.
\url{https://doi.org/10.1007/978-3-642-20267-4_10}.

\bibitem[\citeproctext]{ref-guinness2021gpgp}
Guinness, Joseph, Matthias Katzfuss, and Youssef Fahmy. 2021. {``{GpGp}:
Fast {G}aussian Process Computation Using {V}ecchia's Approximation.''}
R package.

\bibitem[\citeproctext]{ref-hall1989polynomial}
Hall, Peter. 1989. {``On Polynomial-Based Projection Indices for
Exploratory Projection Pursuit.''} \emph{The Annals of Statistics} 17
(2): 589--605. \url{https://doi.org/10.1214/aos/1176347127}.

\bibitem[\citeproctext]{ref-huber85}
Huber, Peter J. 1985. {``Projection Pursuit.''} \emph{The Annals of
Statistics} 13 (2): 435--75.
\url{https://doi.org/10.1214/aos/1176349519}.

@@

\bibitem[\citeproctext]{ref-karvonen2023asymptotic}
Karvonen, Toni. 2023. {``Asymptotic Bounds for Smoothness Parameter
Estimates in {G}aussian Process Interpolation.''} \emph{SIAM/ASA Journal
on Uncertainty Quantification} 11 (4): 1225--57.
\url{https://doi.org/10.1137/22M149288X}.

@@

\bibitem[\citeproctext]{ref-laa_using_2020}
Laa, Ursula, and Dianne Cook. 2020. {``Using Tours to Visually
Investigate Properties of New Projection Pursuit Indexes with
Application to Problems in Physics.''} \emph{Computational Statistics}
35 (3): 1171--1205. \url{https://doi.org/10.1007/s00180-020-00954-8}.

\bibitem[\citeproctext]{ref-lee2010projection}
Lee, Eun-Kyung, and Dianne Cook. 2010. {``A Projection Pursuit Index for
Large {\(p\)} Small {\(n\)} Data.''} \emph{Statistics and Computing} 20
(3): 381--92. \url{https://doi.org/10.1007/s11222-009-9131-1}.

\bibitem[\citeproctext]{ref-lee2005projection}
Lee, Eun-Kyung, Dianne Cook, Sigbert Klinke, and Thomas Lumley. 2005.
{``Projection Pursuit for Exploratory Supervised Classification.''}
\emph{Journal of Computational and Graphical Statistics} 14 (4):
831--46. \url{https://doi.org/10.1198/106186005X77702}.

\bibitem[\citeproctext]{ref-Loperfido2018}
Loperfido, Nicola. 2018. {``Skewness-Based Projection Pursuit: A
Computational Approach.''} \emph{Computational Statistics and Data
Analysis} 120 (C): 42--57.
\url{https://doi.org/10.1016/j.csda.2017.11.001}.

@@

\bibitem[\citeproctext]{ref-marie-sainte2010}
Marie-Sainte, Souad Larabi, Alain Berro, and Anne Ruiz-Gazen. 2010.
{``An Efficient Optimization Method for Revealing Local Optima of
Projection Pursuit Indices.''} In \emph{Swarm Intelligence}, edited by
Marco Dorigo, Mauro Birattari, Gianni A. Di Caro, René Doursat, Andries
P Engelbrecht, Dario Floreano, Luca Maria Gambardella, et al., 60--71.
Berlin, Heidelberg: Springer Berlin Heidelberg.
\url{https://doi.org/10.1007/978-3-642-15461-4_6}.

\bibitem[\citeproctext]{ref-cassowaryr}
Mason, Harriet, Stuart Lee, Ursula Laa, and Dianne Cook. 2022.
\emph{Cassowaryr: Compute Scagnostics on Pairs of Numeric Variables in a
Data Set}. \url{https://CRAN.R-project.org/package=cassowayr}.

\bibitem[\citeproctext]{ref-patchwork}
Pedersen, Thomas Lin. 2024. \emph{Patchwork: The Composer of Plots}.
\url{https://CRAN.R-project.org/package=patchwork}.

\bibitem[\citeproctext]{ref-porcu2024matern}
Porcu, Emilio, Moreno Bevilacqua, Robert Schaback, and Chris Oates.
2024. {``The {M}atérn Model: A Journey Through Statistics, Numerical
Analysis and Machine Learning.''} \emph{Statistical Science} 39 (3):
469--92. \url{https://doi.org/10.1214/24-STS923}.

\bibitem[\citeproctext]{ref-posse95}
Posse, Christian. 1995. {``Projection Pursuit Exploratory Data
Analysis.''} \emph{Computational Statistics and Data Analysis} 20 (6):
669--87. \url{https://doi.org/10.1016/0167-9473(95)00002-8}.

@@

\bibitem[\citeproctext]{ref-rajwar_exhaustive_2023}
Rajwar, Kanchan, Kusum Deep, and Swagatam Das. 2023. {``An Exhaustive
Review of the Metaheuristic Algorithms for Search and Optimization:
Taxonomy, Applications, and Open Challenges.''} \emph{Artificial
Intelligence Review}, 1--71.
\url{https://doi.org/10.1007/s10462-023-10470-y}.

\bibitem[\citeproctext]{ref-rasmussen2006gaussian}
Rasmussen, Carl Edward, and Christopher K. I. Williams. 2006.
\emph{Gaussian Processes for Machine Learning}. The MIT Press.

\bibitem[\citeproctext]{ref-broom}
Robinson, David, Alex Hayes, and Simon Couch. 2024. \emph{Broom: Convert
Statistical Objects into Tidy Tibbles}.
\url{https://CRAN.R-project.org/package=broom}.

@@

\bibitem[\citeproctext]{ref-Laa:2020wkm}
Ursula Laa, Andreas Buja, Dianne Cook, and German Valencia. 2022.
{``Hole or Grain? A Section Pursuit Index for Finding Hidden Structure
in Multiple Dimensions.''} \emph{Journal of Computational and Graphical
Statistics} 31 (3): 739--52.
\url{https://doi.org/10.1080/10618600.2022.2035230}.

\bibitem[\citeproctext]{ref-ggh4x}
van den Brand, Teun. 2024. \emph{Ggh4x: Hacks for 'Ggplot2'}.
\url{https://CRAN.R-project.org/package=ggh4x}.

\bibitem[\citeproctext]{ref-tidyverse}
Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.

\bibitem[\citeproctext]{ref-tourr}
Wickham, H., D. Cook, H. Hofmann, and A. Buja. 2011. {``{tourr}: An {R}
Package for Exploring Multivariate Data with Projections.''}
\emph{Journal of Statistical Software} 40 (2): 1--18.
\url{https://doi.org/10.18637/jss.v040.i02}.

@@

\bibitem[\citeproctext]{ref-WW08}
Wilkinson, Leland, and Graham Wills. 2008. {``Scagnostics
Distributions.''} \emph{Journal of Computational and Graphical
Statistics} 17 (2): 473--91.
\url{https://doi.org/10.1198/106186008X320465}.

\bibitem[\citeproctext]{ref-RJ-2021-105}
Zhang, H. Sherry, Dianne Cook, Ursula Laa, Nicolas Langrené, and
Patricia Menéndez. 2021. {``Visual Diagnostics for Constrained
Optimisation with Application to Guided Tours.''} \emph{The R Journal}
13: 624--41. \url{https://doi.org/10.32614/RJ-2021-105}.

\bibitem[\citeproctext]{ref-kabelextra}
Zhu, Hao. 2024. \emph{kableExtra: Construct Complex Table with 'Kable'
and Pipe Syntax}. \url{https://CRAN.R-project.org/package=kableExtra}.

>>>>

Optimisation of PP is often discussed when new indexes are proposed
(Posse 1995; Marie-Sainte, Berro, and Ruiz-Gazen 2010; Grochowski and
Duch 2011). Cook et al. (1995) tied the optimisation more closely to the
index, when they introduced the PPGT, which monitors the optimisation
visually so that the user can see the projected data leading in and out
of the optimum. An implementation is available in the \texttt{tourr}
package (Wickham et al. 2011) in R (R Core Team 2023). Zhang et al.
(2021) illustrated how to diagnose optimisation processes, particularly
focusing on the guided tour, and revealed a need for improved
optimisation. While improving the quality of the optimisation solutions
in the tour is essential, it is also important to be able to view the
data projections as the optimisation progresses. Integrating the guided
tour with a global optimisation algorithm that is efficient in finding
the global optimal and enables viewing of the projected data during the
exploration process is a goal.

@@

There are numerous PP index functions available: introduced in Huber
(1985), Cook, Buja, and Cabrera (1993), Lee et al. (2005), Lee and Cook
(2010), Grimm (2016), Laa et al. (2022). Most are relatively simply
defined, for any projection dimension, and implemented because they are
relatively easy to optimise. A goal is to develop PP indexes based on
scagnostics Wilkinson and Wills (2008), but the blockage is their
optimisation as these tend to be noisy, with potentially small squint
angles.

@@

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, breakable, left=2mm, bottomtitle=1mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, titlerule=0mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, toprule=.15mm, rightrule=.15mm, toptitle=1mm, opacityback=0, bottomrule=.15mm, arc=.35mm, leftrule=.75mm]

@@

The R packages used in this work include: \texttt{tidyr} (Wickham,
Vaughan, and Girlich 2024), \texttt{dplyr} (Wickham et al. 2023),
\texttt{ggplot2} (Wickham 2016), \texttt{knitr} (Xie
2014),\texttt{gtsummary} (Sjoberg et al. 2021), \texttt{patchwork}
(Pedersen 2024), \texttt{ggh4x} (Van Den Brand 2024), \texttt{broom}
(Robinson, Hayes, and Couch 2024), \texttt{kableExtra} (Zhu 2024),
\texttt{ferrn} (Zhang et al. 2021), and \texttt{cassowaryr} (Mason et
al. 2022).

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-abdulah2023large}
Abdulah, S., Y. Li, J. Cao, H. Ltaief, D. Keyes, M. Genton, and Y. Sun.
2023. {``Large-Scale Environmental Data Science with {ExaGeoStatR}.''}
\emph{Environmetrics} 34 (1): e2770.
\url{https://doi.org/10.1002/env.2770}.

\bibitem[\citeproctext]{ref-adams2003sobolev}
Adams, R., and J. Fournier. 2003. \emph{Sobolev Spaces}. Vol. 140. Pure
and Applied Mathematics. Elsevier.

\bibitem[\citeproctext]{ref-Allaire_Quarto_2022}
Allaire, J. J., C. Teague, C. Scheidegger, Y. Xie, and C. Dervieux.
2022. \emph{{Quarto}} (version 1.2).
\url{https://doi.org/10.5281/zenodo.5960048}.

\bibitem[\citeproctext]{ref-Bertsimas93}
Bertsimas, D., and J. Tsitsiklis. 1993. {``Simulated Annealing.''}
\emph{Statistical Science} 8 (1): 10--15.
\url{https://doi.org/10.1214/ss/1177011077}.

\bibitem[\citeproctext]{ref-chou_novel_2021}
Chou, J.-S., and D.-N. Truong. 2021. {``A Novel Metaheuristic Optimizer
Inspired by Behavior of Jellyfish in Ocean.''} \emph{Applied Mathematics
and Computation} 389 (January): 125535.
\url{https://doi.org/10.1016/j.amc.2020.125535}.

@@

\bibitem[\citeproctext]{ref-Grimm2016}
Grimm, K. 2016. {``Kennzahlenbasierte Grafikauswahl.''} Doctoral thesis,
Universität Augsburg.

\bibitem[\citeproctext]{ref-grochowski2011}
Grochowski, M., and W. Duch. 2011. {``Fast Projection Pursuit Based on
Quality of Projected Clusters.''} In \emph{Adaptive and Natural
Computing Algorithms}, edited by A. Dobnikar, U. Lotrič, and B. Šter,
89--97. Berlin, Heidelberg: Springer Berlin Heidelberg.
\url{https://doi.org/10.1007/978-3-642-20267-4_10}.

\bibitem[\citeproctext]{ref-guinness2021gpgp}
Guinness, J., M. Katzfuss, and Y. Fahmy. 2021. {``{GpGp}: Fast
{G}aussian Process Computation Using {V}ecchia's Approximation.''} R
package. \url{https://cran.r-project.org/package=GpGp}.

\bibitem[\citeproctext]{ref-hall1989polynomial}
Hall, P. 1989. {``On Polynomial-Based Projection Indices for Exploratory
Projection Pursuit.''} \emph{The Annals of Statistics} 17 (2): 589--605.
\url{https://doi.org/10.1214/aos/1176347127}.

\bibitem[\citeproctext]{ref-huber85}
Huber, P. J. 1985. {``Projection Pursuit.''} \emph{The Annals of
Statistics} 13 (2): 435--75.
\url{https://doi.org/10.1214/aos/1176349519}.

@@

\bibitem[\citeproctext]{ref-karvonen2023asymptotic}
Karvonen, T. 2023. {``Asymptotic Bounds for Smoothness Parameter
Estimates in {G}aussian Process Interpolation.''} \emph{SIAM/ASA Journal
on Uncertainty Quantification} 11 (4): 1225--57.
\url{https://doi.org/10.1137/22M149288X}.

@@

\bibitem[\citeproctext]{ref-laa_using_2020}
Laa, U., and D. Cook. 2020. {``Using Tours to Visually Investigate
Properties of New Projection Pursuit Indexes with Application to
Problems in Physics.''} \emph{Computational Statistics} 35 (3):
1171--1205. \url{https://doi.org/10.1007/s00180-020-00954-8}.

\bibitem[\citeproctext]{ref-Laa:2020wkm}
Laa, U., D. Cook, A. Buja, and G. Valencia. 2022. {``Hole or Grain? A
Section Pursuit Index for Finding Hidden Structure in Multiple
Dimensions.''} \emph{Journal of Computational and Graphical Statistics}
31 (3): 739--52. \url{https://doi.org/10.1080/10618600.2022.2035230}.

\bibitem[\citeproctext]{ref-lee2010projection}
Lee, E.-K., and D. Cook. 2010. {``A Projection Pursuit Index for Large
\(p\) Small \(n\) Data.''} \emph{Statistics and Computing} 20 (3):
381--92. \url{https://doi.org/10.1007/s11222-009-9131-1}.

\bibitem[\citeproctext]{ref-lee2005projection}
Lee, E.-K., D. Cook, S. Klinke, and T. Lumley. 2005. {``Projection
Pursuit for Exploratory Supervised Classification.''} \emph{Journal of
Computational and Graphical Statistics} 14 (4): 831--46.
\url{https://doi.org/10.1198/106186005X77702}.

\bibitem[\citeproctext]{ref-Loperfido2018}
Loperfido, N. 2018. {``Skewness-Based Projection Pursuit: A
Computational Approach.''} \emph{Computational Statistics and Data
Analysis} 120 (C): 42--57.
\url{https://doi.org/10.1016/j.csda.2017.11.001}.

@@

\bibitem[\citeproctext]{ref-marie-sainte2010}
Marie-Sainte, S. L., A. Berro, and A. Ruiz-Gazen. 2010. {``An Efficient
Optimization Method for Revealing Local Optima of Projection Pursuit
Indices.''} In \emph{Swarm Intelligence}, edited by M. Dorigo, M.
Birattari, G. A. Di Caro, R. Doursat, A. P. Engelbrecht, D. Floreano, L.
M. Gambardella, et al., 60--71. Berlin, Heidelberg: Springer Berlin
Heidelberg. \url{https://doi.org/10.1007/978-3-642-15461-4_6}.

\bibitem[\citeproctext]{ref-cassowaryr}
Mason, H., S. Lee, U. Laa, and D. Cook. 2022. \emph{{c}assowaryr:
Compute Scagnostics on Pairs of Numeric Variables in a Data Set}.
\url{https://CRAN.R-project.org/package=cassowayr}.

\bibitem[\citeproctext]{ref-patchwork}
Pedersen, T. L. 2024. \emph{{p}atchwork: The Composer of Plots}.
\url{https://CRAN.R-project.org/package=patchwork}.

\bibitem[\citeproctext]{ref-porcu2024matern}
Porcu, E., M. Bevilacqua, R. Schaback, and C. Oates. 2024. {``The
{M}atérn Model: A Journey Through Statistics, Numerical Analysis and
Machine Learning.''} \emph{Statistical Science} 39 (3): 469--92.
\url{https://doi.org/10.1214/24-STS923}.

\bibitem[\citeproctext]{ref-posse95}
Posse, C. 1995. {``Projection Pursuit Exploratory Data Analysis.''}
\emph{Computational Statistics and Data Analysis} 20 (6): 669--87.
\url{https://doi.org/10.1016/0167-9473(95)00002-8}.

@@

\bibitem[\citeproctext]{ref-rajwar_exhaustive_2023}
Rajwar, K., K. Deep, and S. Das. 2023. {``An Exhaustive Review of the
Metaheuristic Algorithms for Search and Optimization: Taxonomy,
Applications, and Open Challenges.''} \emph{Artificial Intelligence
Review}, 1--71. \url{https://doi.org/10.1007/s10462-023-10470-y}.

\bibitem[\citeproctext]{ref-rasmussen2006gaussian}
Rasmussen, C. E., and C. K. I. Williams. 2006. \emph{Gaussian Processes
for Machine Learning}. The MIT Press.

\bibitem[\citeproctext]{ref-broom}
Robinson, D., A. Hayes, and S. Couch. 2024. \emph{{b}room: Convert
Statistical Objects into Tidy Tibbles}.
\url{https://CRAN.R-project.org/package=broom}.

\bibitem[\citeproctext]{ref-gtsummary}
Sjoberg, D. D., K. Whiting, M. Curry, J. A. Lavery, and J. Larmarange.
2021. {``Reproducible Summary Tables with the {g}tsummary Package.''}
\emph{{The R Journal}} 13: 570--80.
\url{https://doi.org/10.32614/RJ-2021-053}.

@@

\bibitem[\citeproctext]{ref-ggh4x}
Van Den Brand, T. 2024. \emph{{g}gh4x: Hacks for {ggplot2}}.
\url{https://CRAN.R-project.org/package=ggh4x}.

\bibitem[\citeproctext]{ref-ggplot2}
Wickham, H. 2016. \emph{{g}gplot2: Elegant Graphics for Data Analysis}.
Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}.

\bibitem[\citeproctext]{ref-tourr}
Wickham, H., D. Cook, H. Hofmann, and A. Buja. 2011. {``{t}ourr: An r
Package for Exploring Multivariate Data with Projections.''}
\emph{Journal of Statistical Software} 40 (2): 1--18.
\url{https://doi.org/10.18637/jss.v040.i02}.

\bibitem[\citeproctext]{ref-dplyr}
Wickham, H., R. François, L. Henry, K. Müller, and D. Vaughan. 2023.
\emph{{d}plyr: A Grammar of Data Manipulation}.
\url{https://CRAN.R-project.org/package=dplyr}.

\bibitem[\citeproctext]{ref-tidyr}
Wickham, H., D. Vaughan, and M. Girlich. 2024. \emph{{t}idyr: Tidy Messy
Data}. \url{https://CRAN.R-project.org/package=tidyr}.

@@

\bibitem[\citeproctext]{ref-WW08}
Wilkinson, L., and G. Wills. 2008. {``Scagnostics Distributions.''}
\emph{Journal of Computational and Graphical Statistics} 17 (2):
473--91. \url{https://doi.org/10.1198/106186008X320465}.

\bibitem[\citeproctext]{ref-knitr}
Xie, Y. 2014. {``{k}nitr: A Comprehensive Tool for Reproducible Research
in {R}.''} In \emph{Implementing Reproducible Computational Research},
edited by V. Stodden, F. Leisch, and R. D. Peng. Chapman; Hall/CRC.

\bibitem[\citeproctext]{ref-RJ-2021-105}
Zhang, H. S., D. Cook, U. Laa, N. Langrené, and P. Menéndez. 2021.
{``Visual Diagnostics for Constrained Optimisation with Application to
Guided Tours.''} \emph{The R Journal} 13: 624--41.
\url{https://doi.org/10.32614/RJ-2021-105}.

\bibitem[\citeproctext]{ref-kabelextra}
Zhu, H. 2024. \emph{{k}ableExtra: Construct Complex Table with {kable}
and Pipe Syntax}. \url{https://CRAN.R-project.org/package=kableExtra}.
